\LARGE \bf Explicit Knowledge and the Deliberative Layer: Lessons Learned

### 2013-07-08 paper.tex
Remove the section on the blind and deaf robot

We believe that this \emph{knowledge-oriented} approach has a strong potential
not only to enable rich human-robot interaction, but also as a broader approach
to information alignment and fusion in complex robotic systems.  The
versatility of this paradigm could be illustrated by a simple imaginary
scenario with a blind robot and a deaf robot. The blind robot does not see (no
cameras or alike), but someone can verbally describe a scene to it. On the
other hand, the deaf robot has a good vision system, but cannot process verbal
input.  Without any changes to the software architecture that we described,
control modules of both robots could equally perform the same tasks since all
the knowledge is abstracted and centralised (note that to actually implement
this imaginary situation, the blind robot would of course need \textit{a
priori} 3D models of objects talked about to enable planning or pick and place
actions, and the deaf robot would require at least some gesture interpretation
to understand orders).

>>>>

We believe that this \emph{knowledge-oriented} approach has a strong potential
not only to enable rich human-robot interaction, but also as a broader approach
to information alignment and fusion in complex robotic systems.
